Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-29 latex/comp_or.tex
Paper CompOR update
Finished Comp OR paper

According to \cite{BrandtStefan2019}, {\it Technically the task to solve is a three-dimensional Container Loading Problem (CLP) with a multitude of constraints. The CLP alone is known to be NP-hard and extremely hard to solve even for instances of moderate size. The typical number of items per transport segment ranges between 300 and 800 items.}

@@

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results {\bf before} 3D packing}  \label{tab:results}
	\footnotesize
	%\scriptsize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}      &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule	
		\multirow{7}{*}{$1.2$}&$Relaxed$  & $f$                &{\it 12.23}&{\it 8.67} &{\it 12.67}&{\it 15.36}&{\it 16.29}&{\it 16.20}& - \\%  
		&                      $MIP$      & {\it run time (s)} &     3     &     13    &     20    &     78    &      198  &     1103  & - \\% 							
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &     10.34 &{\bf 8.50} &{\bf 12.42}&{\bf 15.06}&{\bf 15.97}&{\bf 15.88}&{\bf 0.97} \\%   best 8079
		&                                 & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.00 \\% 	439		
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 12.96}&   7.53    &  12.28    &   13.20   &  13.71    &   13.44   &  0.91\\% 
		&                                 & {\it run time (s)} &     < 1   &     2     &     2     &     8     &     22    &     120   &  {\bf 2.80}\\% 155
		\toprule		
		\multirow{7}{*}{$1.5$}&$Relaxed$  & $f$                &{\it 17.01}&{\it 12.45}&{\it 18.02}&{\it 22.03}&{\it 23.09}&{\it 22.35}& - \\%  
		&                       $MIP$     & {\it run time (s)} &     4     &     20    &     32    &     115   &     296   &     1685  &  -\\%					
        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $Shims$}        & $f$                &     14.68 &{\bf 12.21}&{\bf 17.67}&{\bf 21.01}&{\bf 22.64}&{\bf 21.91}&{\bf 0.99}  \\%  best 11156
        &                                 & {\it run time (s)} &     < 1   &     2     &     3     &     12    &     33    &   209     &  1.00 \\% 
        \cmidrule{2-10}		                      
        &\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 16.12}&     11.81 &     17.48 &  17.66    &   19.81   &  17.61    &  0.90 \\% 
        &                                 & {\it run time (s)} &     < 1   &     1     &     2     &     7     &   20      &  120      &  {\bf 1.70}\\% 
		\toprule
		\multirow{7}{*}{$2.0$}&$Relaxed$  & $f$                &{\it 24.56}&{\it 17.47}&{\it 25.19}&{\it 27.94}&{\it 29.90}&{\it 27.60}& -\\%  
		&                       $MIP$     & {\it run time (s)} &     4     &     23    &    34     &   119     &     317      &           & -\\%							
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &    21.31  &{\bf 17.35}&   24.24   &{\bf 27.39}&{\bf 29.31}&{\bf 27.06}&{\bf 0.98}  \\%  best 15014
		&                                 & {\it run time (s)} &     < 1   &     2     &     4     &     14    &     35    &   220     &  1.00 \\% 
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 24.33}&   17.26   &{\bf 24.70}&   24.81   &   27.71   &  24.93    &  0.96  \\% 
		&                                 & {\it run time (s)} &     < 1   &     2     &     3     &     9     &   26      &  151      &  {\bf 1.70}\\% 
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

@@

Table \ref{tab:results2} presents the results of the MIP solver compared to {\it Shims} and {\it mpShims}, after the post-optimization with the multiprocessing 3D packing.

Although the relaxed MIP solver results are not always feasible, the multiprocessing 3D packing turns them feasible regarding dimensions and weight. So, in Table \ref{tab:results2}, we considered it's results in the performance comparisons.

\vspace{2.0mm}
\begin{table}[H]
	\centering
\color{blue}{	
	\caption{Volume surpluses, methods and scenarios results {\bf after} 3D packing}  \label{tab:results2}
}
	\footnotesize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                    &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}      &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule
		\multirow{7}{*}{$1.2$}&$Relaxed$  & $f$                &   11.47   &    7.24   &{\bf 10.78}&     12.06 &     12.97 &    12.44  &     0.95 \\%
		&                       $MIP$     & {\it run time (s)} &     6     &     25    &     41    &     158   &      401  &     2161  &{\bf 1.70}\\% 2792					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &    9.05   &   5.11    &   9.75    &   10.96   &   12.86   &   13.25   &     0.86 \\% 
		&                                 & {\it run time (s)} &     16    &     68    &     94    &    323    &    719    &    3549   &     1.00 \\% 	4769		
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 12.14}&{\bf 7.29} &   10.36   &{\bf 12.63}&{\bf 14.04}&{\bf 13.92}&{\bf 0.99}\\% best 7080
		&                                 & {\it run time (s)} &     9     &     36    &     54    &     192   &     427   &    2118   &{\bf 1.70}\\%	2836	
		\toprule		
		\multirow{7}{*}{$1.5$}&$Relaxed$  & $f$                &     15.83 &{\bf 10.08}&{\bf 15.14}&{\bf 16.87}&     18.58 &     17.52 &     0.97 \\%  
		&                      $MIP$      & {\it run time (s)} &    10     &     43    &     72    &     262   &     696   &     3741  &{\bf 1.60} \\% 4824					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   11.55   &   7.61    &   12.28   &   15.00   &   17.55   &   17.57   &  0.84  \\%  
		&                                 & {\it run time (s)} &    25     &    107    &     156   &    498    &    1217   &   5743    &  1.00 \\% 7746
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 17.05}&   10.01   &   15.01   &   16.75   &{\bf 20.09}&{\bf 17.85}&{\bf 1.00} \\%   best 9708
		&                                 & {\it run time (s)} &    18     &    64     &     101   &    351    &   828     &  3879     &     1.50\\% 5421
		\toprule
		\multirow{7}{*}{$2.0$}&$Relaxed$  & $f$                &     23.73 &{\bf 15.23}&   21.96   &   24.22   &   26.69   &           &  {\bf 1.00} \\%  
		&                       $MIP$     & {\it run time (s)} &    14     &     59    &     95    &    348    &   880     &         &  1.00 \\% 					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   16.28   &   10.93   &   18.16   &   22.35   &   25.12   &   24.53    &   0.96  \\%  
		&                                 & {\it run time (s)} &    37     &    141    &   196     &     653   &   1453    &   6851     &  1.00 \\% 
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 24.52}&   15.18   &{\bf 21.99}&{\bf 24.61}&{\bf 26.94}&   24.83    &  0.94  \\% 
		&                                 & {\it run time (s)} &    27     &    87     &   146     &    496    &   1080    &   5160     &  {\bf 1.70}\\% 
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

>>>>

According to \cite{BrandtStefan2019}, {\it Technically the task to solve is a three-dimensional Container Loading Problem (CLP) with a multitude of constraints. The CLP alone is known to be NP-hard and extremely hard to solve even for instances of moderate size. The typical number of items per transport segment ranges between 300 and 800 items.} This work also adopts a similar range as items quantities, from 300 to 1000 items per node.

@@

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results {\bf before} 3D packing}  \label{tab:results}
	\footnotesize
	%\scriptsize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}      &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule	
		\multirow{7}{*}{$1.2$}&$Relaxed$  & $f$                &{\it 12.23}&{\it 8.67} &{\it 12.67}&{\it 15.36}&{\it 16.29}&{\it 16.20}& - \\%  
		&                      $MIP$      & {\it run time (s)} &     3     &     13    &     20    &     78    &      198  &     1103  & - \\% 							
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &     10.34 &{\bf 8.50} &{\bf 12.42}&{\bf 15.06}&{\bf 15.97}&{\bf 15.88}&{\bf 0.97} \\%   best 8079
		&                                 & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.00 \\% 	439		
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 12.96}&   7.53    &  12.28    &   13.20   &  13.71    &   13.44   &  0.91\\% 
		&                                 & {\it run time (s)} &     < 1   &     2     &     2     &     8     &     22    &     120   &  {\bf 2.80}\\% 155
		\toprule		
		\multirow{7}{*}{$1.5$}&$Relaxed$  & $f$                &{\it 17.01}&{\it 12.45}&{\it 18.02}&{\it 22.03}&{\it 23.09}&{\it 22.35}& - \\%  
		&                       $MIP$     & {\it run time (s)} &     4     &     20    &     32    &     115   &     296   &     1685  &  -\\%					
        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $Shims$}        & $f$                &     14.68 &{\bf 12.21}&{\bf 17.67}&{\bf 21.01}&{\bf 22.64}&{\bf 21.91}&{\bf 0.99}  \\%  best 11156
        &                                 & {\it run time (s)} &     < 1   &     2     &     3     &     12    &     33    &   209     &  1.00 \\% 
        \cmidrule{2-10}		                      
        &\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 16.12}&     11.81 &     17.48 &  17.66    &   19.81   &  17.61    &  0.90 \\% 
        &                                 & {\it run time (s)} &     < 1   &     1     &     2     &     7     &   20      &  120      &  {\bf 1.70}\\% 
		\toprule
		\multirow{7}{*}{$2.0$}&$Relaxed$  & $f$                &{\it 24.56}&{\it 17.47}&{\it 25.19}&{\it 27.94}&{\it 29.90}&{\it 27.60}& -\\%  
		&                       $MIP$     & {\it run time (s)} &     4     &     23    &    34     &   119     &     317      &   1762        & -\\%							
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &    21.31  &{\bf 17.35}&   24.24   &{\bf 27.39}&{\bf 29.31}&{\bf 27.06}&{\bf 0.98}  \\%  best 15014
		&                                 & {\it run time (s)} &     < 1   &     2     &     4     &     14    &     35    &   220     &  1.00 \\% 
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 24.33}&   17.26   &{\bf 24.70}&   24.81   &   27.71   &  24.93    &  0.96  \\% 
		&                                 & {\it run time (s)} &     < 1   &     2     &     3     &     9     &   26      &  151      &  {\bf 1.70}\\% 
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

@@

Table \ref{tab:results2} presents the results of the {\it Relaxed MIP solver} compared to {\it Shims} and {\it mpShims}, after the post-optimization with the multiprocessing 3D packing.

Although the {\it Relaxed MIP solver} results are not always feasible, the multiprocessing 3D packing turns them feasible regarding dimensions and weight. So, in Table \ref{tab:results2}, we considered it's results in the performance comparisons.

\vspace{2.0mm}
\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results {\bf after} 3D packing}  \label{tab:results2}
	\footnotesize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                    &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}      &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule
		\multirow{7}{*}{$1.2$}&$Relaxed$  & $f$                &   11.47   &    7.24   &{\bf 10.78}&     12.06 &     12.97 &    12.44  &     0.95 \\%
		&                       $MIP$     & {\it run time (s)} &     12     &     51    &     81    &     258   &      601  &     3161  &{\bf 1.15}\\% 	4164				
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &    9.05   &   5.11    &   9.75    &   10.96   &   12.86   &   13.25   &     0.86 \\% 
		&                                 & {\it run time (s)} &     16    &     68    &     94    &    323    &    719    &    3549   &     1.00 \\% 	4769		
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 12.14}&{\bf 7.29} &   10.36   &{\bf 12.63}&{\bf 14.04}&{\bf 13.92}&{\bf 0.99}\\% best 7080
		&                                 & {\it run time (s)} &     9     &     36    &     54    &     192   &     427   &    2118   &{\bf 1.70}\\%	2836	
		\toprule		
		\multirow{7}{*}{$1.5$}&$Relaxed$  & $f$                &     15.83 &{\bf 10.08}&{\bf 15.14}&{\bf 16.87}&     18.58 &     17.52 &     0.97 \\%  
		&                      $MIP$      & {\it run time (s)} &    20     &     83    &     142   &     362   &     996   &     4741  &{\bf 1.22} \\% 6344					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   11.55   &   7.61    &   12.28   &   15.00   &   17.55   &   17.57   &     0.84  \\%  
		&                                 & {\it run time (s)} &    25     &    107    &     156   &    498    &    1217   &   5743    &     1.00  \\% 7746
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 17.05}&   10.01   &   15.01   &   16.75   &{\bf 20.09}&{\bf 17.85}&{\bf 1.00} \\%   best 9708
		&                                 & {\it run time (s)} &    18     &    64     &     101   &    351    &   828     &  3879     &     1.50  \\% 5421
		\toprule
		\multirow{7}{*}{$2.0$}&$Relaxed$  & $f$                &     23.73 &{\bf 15.23}&   21.96   &   24.22   &   26.69   &    24.29  &     0.99  \\%  
		&                       $MIP$     & {\it run time (s)} &    28     &     99    &     185   &    648    &   1680    &   8774    &     1.00  \\% 11414					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   16.28   &   10.93   &   18.16   &   22.35   &   25.12   &   24.53   &     0.85  \\%  
		&                                 & {\it run time (s)} &    37     &    141    &   196     &     653   &   1453    &   6851    &     1.22  \\% 9331
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 24.52}&   15.18   &{\bf 21.99}&{\bf 24.61}&{\bf 26.94}&{\bf 24.83}&{\bf 1.00} \\% best 13812
		&                                 & {\it run time (s)} &    27     &    87     &   146     &    496    &   1080    &   5160    &     1.63  \\% 6996
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

The average value of $f$ obtained by {\it mpShims} was 0.997, followed by the {\it Relaxed MIP} with 0.971.  {\it Shims} obtained 0.851, on average.

As to the performance, the average {\bf Speedup} obtained by {\it mpShims} was 1.61, followed by the {\it Relaxed MIP} with 1.12. {\it Shims} reached 1.07, on average.

So, in terms of quality and speed, {\it mpShims} with the {\it Multiprocessing 3D packing} was the best method to solve the ACLP-RPDP.
